Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays

### 2019-04-09 reports/paper1/paper.tex
Paper revision

\documentclass[twocolumn]{article}

@@

\subsection{Apparatus and Procedures}

@@

The empirical null filter was implemented using \texttt{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$. a) X-ray image with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroisep16120deg_inference_radius4}
\end{figure*}

>>>>

\documentclass{proc}

@@

\subsection{Apparatus and Data Collection}

@@

The empirical null filter was implemented using \texttt{ImageJ} \citep{abramoff2004image, schindelin2012fiji, schneider2012nih, perez2013image} by modifying the existing class \texttt{RankFilters}. It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads. Each thread filters a row in parallel.

Line filtering was done from left to right. At the start on the far left, an initial value of the median of all the pixels in the kernel was used. For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as a initial point. This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.

When filtering a pixel, the Newton-Raphson method was used to solve for $\widehat{\mu}_{0,x,y}=z$
\begin{equation}
  \dfrac{\partial}{\partial z}\ln\widehat{p}_{Z_{x,y}}(z) = 0
\end{equation}
by using the iterative procedure
\begin{equation}
  z^{(r+1)} =
  z^{(r)}
  -\dfrac{
    \left.
      \dfrac{
        \partial
      }
      {
        \partial z
      }
      \ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z = z^{(r)}}
  }
  {
    \left.
      \dfrac{
        \partial^2
      }
      {
        \partial z^2
      }
      \ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z = z^{(r)}}
  } 
\end{equation}
where $z^{(0)}$ is the initial value. A convergence criteria was met when either 10 update steps were taken or when
\begin{equation}
  \log\left[\left|
    \left.
    \dfrac{
      \partial
    }
    {
      \partial z
    }
  \ln\widehat{p}_{x,y}(z)
  \right|_{z=z^{(r)}}
  \right|\right]
  <-5
\end{equation}
at the current step. This was chosen arbitrary to speed up the algorithm without losing too much accuracy. The solution is valid if
\begin{equation}
  \left.
    \dfrac{
      \partial^2
    }
    {
      \partial z^2
    }
    \ln\widehat{p}_{Z_{x,y}}(z)
  \right|_{z=\widehat{\mu}_{0,x,y}}
  < 0 \ .
\end{equation}
Further initial values were generated by sampling from $\normal(z^{(0)}, s_{x,y}^2)$. This was done multiple times until 3 valid solutions were obtained. The best solution, the one with the largest $\ln\widehat{p}_{Z_{x,y}}\left(\widehat{\mu}_{0,x,y}\right)$, out of all the different initial values was used as the final answer.

@@

\begin{figure*}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_sig.eps}
        \caption{X-ray image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiSep16120deg_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\addNumber{../figures/inference/DefectDetectSubRoiSep16120deg_radius4.txt}$. a) X-ray image with highlighted red positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroisep16120deg_inference_radius4}
\end{figure*}
